\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-01-28 paper.tex
new

@@

>>>>

We

@@

\subsection{Uniformity}

(Give a set of parameters)
We firstly need to propose a way of measuring uniformity.
Then we can apply it to compare MCMC approach with rejection sampling and hierarchical rejection sampling.
We are interested with
\begin{itemize}
	\item asymptotic behavior (assumption: MCMC converge to a close uniformity)
	\item convergence rate (assumption: MCMC converge faster)
\end{itemize}

\subsection{Efficiency}

The efficiency is shown by how the time is needed when the number of nodes are increased.
(Y: time spent) and (X: number of nodes).

\subsection{Integration}

We're going to test with RRT*, which falls into a informed RRT*.

We are going to show how the solution cost falls along time.
(Y: solution cost) and (X: time spent).

\begin{itemize}
\item DIMT (double integrator minimum time)
\item Dubins car
\item Airplane
\end{itemize}
